---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# legihelpR

<!-- badges: start -->
<!-- badges: end -->

This R package, legihelpR, is meant to use the legiscan API to help track legislative actions.

## Installation & Load

You can install the development version of legihelpR from [GitHub](https://github.com/aberuiz/legihelpR) with:

```{r}
# install.packages("remotes")
# remotes::install_github("aberuiz/legihelpR")
library(legihelpR)
```

## API Registration

Requests to legiscan require an API key to function. You can register for an API key on the [legiscan website](https://legiscan.com/user/register).

You can store your API key into your environment using `setlegiKey`. To permanently store your legiscan API key in your environment use the argument 'install = TRUE'.

```{r eval = FALSE}
setlegiKey(
  APIkey = "< 32 character API Key >",
  install = TRUE
)
```

Once you have set up your API key all other legihelpR functions will use `getlegiKey` to check your stored environment file by default.
You can use `getlegiKey` to check which API key you have stored. 
You can overwrite your existing key by using 'overwrite = TRUE' in `setlegiKey`.

## Sessions

Receive a dataframe of all sessions in legiscan's database using `getSessions` to return unique Session IDs for the provided state.

```{r}
getSessions(state = "MA")
```

## Master List

For receiving a Master List from legiscan's API you can use `getMasterlist`. You can provide a unique session ID or you can provide the state abbreviation to return the most recent regular session from that state.

```{r}
getMasterList(session = 2108)
```
