---
title: "Detecting Bill Changes with change_hash"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Detecting Bill Changes with change_hash}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r setup}
library(legihelpR)
```

If you track a legislative session over time, the naive approach — re-fetching
every bill you care about on a schedule — burns through your LegiScan quota
(30,000 queries/month) fast. A session with 5,000 bills polled daily is
150,000 queries a month before you've done anything useful.

LegiScan's API is built for a cheaper pattern, described in the API manual's
*Update Workflow* section: every bill record carries a `change_hash` that
changes whenever anything about the bill changes. `getMasterListRaw` returns
the `bill_id` and `change_hash` for an entire session in a **single query**.
By keeping the hashes from your last check and comparing, you can identify
exactly which bills changed and re-fetch only those with `getBill`.

The daily cost becomes: 1 query for the master list + 1 query per bill that
actually changed. For most sessions on most days, that's a handful of queries
instead of thousands.

## Step 1 — Establish a baseline

Pull the raw master list for the session you're tracking (find session IDs
with `getSessions`) and store it locally. `saveRDS` is the simplest store;
a database table works the same way if you're already using one.

```{r baseline}
sessionID <- 2108

baseline <- getMasterListRaw(sessionID = sessionID)

saveRDS(baseline, "bill_hashes.rds")
```

If you want the full bill detail up front — not just the hashes — you can
bulk-load the session once from a weekly dataset archive instead. `getDatasetList`
shows what's available and `getDataset(file = ...)` writes the ZIP of JSON bill
records to disk. The archive costs one query no matter how many bills the
session has.

```{r bulk-load}
datasets <- getDatasetList(state = "TX")

getDataset(
  sessionID = datasets$session_id[1],
  accessKey = datasets$access_key[1],
  file = "session_archive.zip"
)
```

## Step 2 — Check for changes

On whatever schedule suits you (daily is typical), fetch the master list again
— one query — and join it against the stored hashes. Three cases fall out:
new bills, changed bills, and (rarely) bills that dropped off the list.

```{r diff}
stored <- readRDS("bill_hashes.rds")
current <- getMasterListRaw(sessionID = sessionID)

comparison <- current |>
  dplyr::left_join(
    stored |> dplyr::select(bill_id, old_hash = change_hash),
    by = "bill_id"
  )

newBills <- comparison |> dplyr::filter(is.na(old_hash))
changedBills <- comparison |> dplyr::filter(!is.na(old_hash), change_hash != old_hash)

message(nrow(newBills), " new, ", nrow(changedBills), " changed")
```

## Step 3 — Re-fetch only what changed

Each changed or new bill costs one `getBill` query. On a quiet day this loop
does nothing at all.

```{r refetch}
toFetch <- c(newBills$bill_id, changedBills$bill_id)

updatedBills <- lapply(toFetch, \(id) getBill(billID = id))
```

`getBill` returns the full bill record — status, progress, sponsors, votes,
and document metadata — so whatever you store downstream can be refreshed from
it. If you also archive bill text, the record's `texts` element carries a
`doc_id` for each version; pass it to `getText(textID = ..., file = ...)` to
write the document to disk.

## Step 4 — Save the new baseline

Overwrite the stored hashes so the next run diffs against today.

```{r save}
saveRDS(current, "bill_hashes.rds")
```

## Variation: keyword monitoring across states

If you're tracking a topic rather than a session, `legiSearchRaw` returns
`bill_id` and `change_hash` for search results — the same diff pattern applies.
Store the hashes from your last search, re-run the search on a schedule, and
`getBill` only the hits that are new or changed.

```{r keyword}
hits <- legiSearchRaw(query = "wage theft", state = "TX")
```

Each page of search results is one query; `legiSearchRaw` paginates
automatically up to `maxPages`.
